Sequential rank agreement methods for comparison of ranked lists

### 2015-05-06 latex/paper.Rnw
Rettelser til tekst

The agreement, $A(X_p)$, cannot be computed directly for all
predictors because we only observe a censored version of $\tilde R$
for some of the lists. Instead we assume that the rank assigned to
item $X_p$ in list $l$ is uniformly distributed among the ranks that
have \emph{not} been assigned for list $l$,
\begin{equation}
\tilde A(X_p) = \frac{\sum_{r_1; r_1\in \tilde R_1(X_p)}  \cdots \sum_{r_L; r_L\in \tilde R_L(X_p)} A(X_p)}{\prod_l |\tilde R_l(X_p)|}.
\end{equation}

The rankings within a single list are clearly not independent since
each of the lists essentially contains full set of ranks and by

>>>>

The agreement, $A(X_p)$, cannot be computed directly for all
predictors because we only observe a censored version of $\tilde R$
for some of the lists. Instead we assume that the rank assigned to
item $X_p$ in list $l$ is uniformly distributed among the ranks that
have \emph{not} been assigned for list $l$, so the augmented agreement
becomes
\begin{equation}
\tilde A(X_p) = \frac{\sum_{r_1; r_1\in \tilde R_1(X_p)}  \cdots
  \sum_{r_L; r_L\in \tilde R_L(X_p)} A(X_p)}{\prod_l |\tilde
  R_l(X_p)|}. \label{formula:censored-agreement}
\end{equation}
Similarly, the sequential rank agreement becomes
\begin{equation}
XXX \textrm{SRA}(d)= \sqrt{\frac{\sum_{\{p \in S_d\}}(L-1)\tilde{A}(X_p)^2}{(L-1)|S_d|}}, \label{def:sra-censored}
\end{equation}

The rankings within a single list are clearly not independent since
each rank must appear exactly in each list. Thus, by randomizing
unobserved items as described in \eqref{formula:censored-agreement}

 ess contains full set of ranks and by using
the ... instead of applying the average ...

the mean then we
